Data Analysis Project

### 2024-06-18 code/eda-code/eda2.qmd
commit changes

Once more height as function of weight, stratified by gender. Note that there is so little data, it's a bit silly. But we'll plot it anyway.

@@

@@

```{r}
p6 <- mydata %>% ggplot(aes(x=age, y=charges)) +
  geom_point(alpha=0.5, color="blue") +
  labs(title="Insurance Charges by Age", x="Age", y="Charges") +
  theme_minimal()
plot(p6)
figure_file = here("results", "figures", "charge-age-boxplot.png")
ggsave(filename = figure_file, plot=p6) 
```

```{r}
p7 <- mydata %>% ggplot(aes(x=bmi, y=charges)) +
  geom_point(alpha=0.5, color="green") +
  labs(title="Insurance Charges by BMI", x="BMI", y="Charges") +
  theme_minimal()
plot(p7)
figure_file = here("results", "figures", "charge-bmi-scatter.png")
ggsave(filename = figure_file, plot=p7) 
```

```{r}
p8 <- mydata %>% ggplot(aes(x=as.factor(children), y=charges, fill=as.factor(children))) +
  stat_summary(fun.y=mean, geom="bar") +
  labs(title="Average Insurance Charges by Number of Children", x="Number of Children", y="Average Charges") +
  theme_minimal()
plot(p8)
figure_file = here("results", "figures", "children-bar.png")
ggsave(filename = figure_file, plot=p8) 
```

>>>>

Now let's look at a boxplot for charges by smoking status

@@

Boxplot for charges by region

@@

Scatter plot for charges by age
```{r}
p6 <- mydata %>% ggplot(aes(x=age, y=charges)) +
  geom_point(alpha=0.5, color="blue") +
  labs(title="Insurance Charges by Age", x="Age", y="Charges") +
  theme_minimal()
plot(p6)
figure_file = here("results", "figures", "charge-age-boxplot.png")
ggsave(filename = figure_file, plot=p6) 
```

Scatter plot for charges by BMI
```{r}
p7 <- mydata %>% ggplot(aes(x=bmi, y=charges)) +
  geom_point(alpha=0.5, color="green") +
  labs(title="Insurance Charges by BMI", x="BMI", y="Charges") +
  theme_minimal()
plot(p7)
figure_file = here("results", "figures", "charge-bmi-scatter.png")
ggsave(filename = figure_file, plot=p7) 
```

Bar Plot if average charges by number of children
```{r}
p8 <- mydata %>% ggplot(aes(x=as.factor(children), y=charges, fill=as.factor(children))) +
  stat_summary(fun.y=mean, geom="bar") +
  labs(title="Average Insurance Charges by Number of Children", x="Number of Children", y="Average Charges") +
  theme_minimal()
plot(p8)
figure_file = here("results", "figures", "children-bar.png")
ggsave(filename = figure_file, plot=p8) 
```

### 2024-06-18 products/manuscript/Manuscript.qmd
commit changes

@@

```{}
```

>>>>

@tbl-resulttable1 shows a simple model with one predictor using linear regression analysis.

```{r}
#| label: tbl-resulttable1
#| tbl-cap: "Simple Models with One Predictor."
#| echo: FALSE
simpletable=readRDS("../../results/tables/simple_models_results.rds")
knitr::kable(simpletable)
```

@@

@tbl-resulttable2 shows linear regression analysis charges is analyzed across all predictors.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear Regression Analysis."
#| echo: FALSE
lineartable=readRDS("../../results/tables/linear_regression_results.rds")
knitr::kable(lineartable)

@fig-linear helps visualize which features have a significant effect on charges.

```{r}
#| label: fig-linear
#| fig-cap: "Linear Regression Coefficients."
#| echo: FALSE
knitr::include_graphics(here("results","figures","linear_regression_plot.png"))

@tbl-resulttable3 helps to capture complex interaction between features.

```{r}
#| label: tbl-resulttable3
#| tbl-cap: "Random Forest Analysis."
#| echo: FALSE
rf_table=readRDS("../../results/tables/random_forest_importance.rds")
knitr::kable(rf_table)
```

@fig-randomforest helps visualize how each feature have a significant effect on charges.

```{r}
#| label: fig-randomforest
#| fig-cap: "Random Forest Feature Importance."
#| echo: FALSE
knitr::include_graphics(here("results","figures","random_forest_importance_plot.png"))
```
